\sysfull

### 2017-11-15 paper/compiler.tex
review of compiler section (second pass)

We studied \sys's effectiveness for systems with automatically generated task
boundaries by developing a simple compiler prototype that transforms an
arbitrary C into a program with tasks. The compiler is representative of,
although not a direct implementation of, a system that assists in writing
task-based programs by automatically inserting tasks (e.g., inspired by
Ratchet~\cite{ratchet}). Translating C code to use tasks requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task or are made explicit with inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime. Our simple prototype, implemented using LLVM, analyzes the control-flow graph (CFG) and uses a rule-based heuristic to determine at which points to place a task boundary. After identifying where to put task
boundaries, the \sys compiler transforms the imperative code into tasks,
instrumenting protected memory accesses.

@@

\sys analyzes a program to determine where to put task boundaries. 
%
A task is single-entry, multiple-exit part of the CFG that \sys compiler excises
into a new function.  
%
There are several factors determining efficient task execution. A task decomposition should minimize the number of variables that are accessed by multiple tasks and, consequently, must be protected by \sys's paging mechanism. 
%
Different tasks should be approximately the same size to make reasoning about
coalescing simple by eliminating the need to consider variable run time costs. 
%
To minimize task boundary overheads (e.g., commit), a task decomposition should
maximize task size, which minimizes the frequency of task transitions.

@@

%
%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.
%

@@

\textbf{Live Variable Cost.} Each CFG edge is associated with a set of
variables that {\em may} be {\em alive} across the edge, i.e., variables
assigned before the edge and may be read after the edge. Variables that live
across an edge must be protected by \sys's memory virtualization mechanism when
\sys places a task boundary on the edge. \sys heuristically minimizes variable
virtualization overhead by placing boundaries to minimize the number of
live variables that span task boundaries.

>>>>

We studied \sys's effectiveness for systems with automatically generated task
boundaries by developing a simple compiler prototype that transforms an
arbitrary C into a program with tasks. The compiler is representative of,
although \emph{not a direct implementation} of, a system that assists in writing
task-based programs by automatically inserting tasks (e.g., inspired by
Ratchet~\cite{ratchet}).

\textbf{Automatic Task Generation Flow.} Transforming C code to use tasks requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task or are made explicit with inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime. Our simple prototype, implemented using LLVM, analyzes the control-flow graph (CFG) and uses a rule-based heuristic to determine where to place a task boundary. After identifying task boundaries placement, the \sys compiler transforms the imperative code into tasks, instrumenting protected memory accesses.

@@

\sys analyzes a program to determine where to put task boundaries. A task is single-entry, multiple-exit part of the CFG that \sys compiler excises into a new function. There are several factors determining efficient task execution. A task decomposition should minimize the number of variables that are accessed by multiple tasks and, consequently, must be protected by \sys's paging mechanism. Different tasks should be approximately the same size to make reasoning about coalescing simple by eliminating the need to consider variable run time costs. To minimize task boundary overheads (e.g., commit), a task decomposition should maximize task size, which minimizes the frequency of task transitions.

@@

%\sys uses a cost-based task boundary placement analysis that considers per-block energy consumption estimates, inter-task variable liveness, and the cost of partitioning loops.

@@

\textbf{Live Variable Cost.} Each CFG edge associates with a set of
variables that {\em may} be {\em alive} across the edge, i.e. variables
assigned before the edge and may be read after the edge. Variables that live
across an edge must be protected by \sys's memory virtualization when
\sys places a task boundary on the edge. \sys heuristically minimizes variable
virtualization overhead by placing boundaries to minimize the number of
live variables that span task boundaries.
